---
title: "HW 7"
author: "Jacob Haussler"
date: "12/10/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# R Markdown
### Consider binary.csv. This is the superset of gre_data.csv that you used in your practice assignment. This data set has the same binary response variable admit (0/1). But it has 3 regressors - gpa, gre and rank. Rank is a categorical variable indicating the rank of the undergraduate institution attended. Fit a logistic regression model on this data.

```{r}
binary <- read.csv("./binary.csv")
dat <- binary
```


1. Fit a logistic regression model on this data. 
```{r}
logistic.model <- glm(admit ~ gpa+gre+as.factor(rank), family=binomial(link='logit'),data=dat)
summary(logistic.model)
```

2. Interpret the regression coefficients.
- The fitted equation is:

              log( ˆπ/1−ˆπ) = −3.449548 + 0.777014gpa + 0.002294gre - 0.560031rank

3. How does the odds of getting admission changes between students attending rank 2 institution vs. rank 3 institution?
```{r}
rank <- 2
rank2 <- 3
pi_hat <- 1/(1 + exp(-(-3.449548 - 0.560031*rank)))
pi_hat
pi_hat2 <- 1/(1 + exp(-(-3.449548 - 0.560031*rank2)))
pi_hat2


```

- Here we can see that the odds of getting in are better when the rank of the institution is 2 compared to 3.  

4. Estimate the admit status of a student who graduated from a rank 3 institution with gre = 760 and gpa = 3.2.

```{r}
rank3 <- 3
gre <- 760
gpa <- 3.2
pi_hat3 <- 1/(1 + exp(-(-3.449548 + 0.777014*gpa + 0.002294*gre - 0.560031*rank3)))
pi_hat3
y_hat <- ifelse(pi_hat3 > 0.5, 1, 0)
y_hat
```

- The student would not be admitted since pi_hat must be above 0.5. 